---
title: "My Dashbord at DACSS"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
---


```{r setup, include=FALSE}
library(flexdashboard) # always
```

<!-- links -->
```{r}
map1link='https://github.com/aditipabal/WI-EUROPE/raw/refs/heads/main/choropleth_map.rds'
viz1=url(map1link)

map2link='https://github.com/aditipabal/WI-EUROPE/raw/refs/heads/main/dot_map.rds'
viz2=url(map2link)

map3link='https://github.com/aditipabal/WI-EUROPE/raw/refs/heads/main/prop_map.rds'
viz3=url(map3link)
```

## Intro {.sidebar}

This dashboard presents three different types of maps visualizing the total number of mobile cellular telephone subscribers across European countries.
The goal is to compare how mobile adoption varies geographically.


## Column {data-width="450"}

Choropleth Map — Mobile Subscribers Distribution

This map uses color intensity to represent the total number of mobile subscribers. Darker shades indicate higher values.

```{r}

readRDS(viz1)
```
Dot Density Map — Subscriber Concentration

Each dot corresponds to a proportion of total mobile subscribers in a country, illustrating concentration and density patterns.
```{r}

readRDS(viz2)
```

## Column {data-width="550"}

Proportional Symbols Map — Comparative Scale

Bubble sizes represent the relative number of mobile subscribers. Larger circles indicate countries with more mobile users.
```{r}
readRDS(viz3)
```

